\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-08-10 paper/paper.tex
Rearrange abstract

\bigskip
\begin{abstract}
% Consumers have an interest in accurate assessment of product reliability.  However, lifetime data is often sparse and has limited information.  
When the information carried by lifetime data are limited by sample size, censoring and truncation, lifetime analysis can suffer from imprecision. These limitations are not atypical; for example, lifetime data for high-reliability products will tend to be right-censored.

With field data on consumer products, model-based approaches to inference require a model with sufficient flexibility to account for multiple kinds of failure. The causes of these, while not interesting to the consumer per se, can lead to various observed lifetime distributions. Because of this, standard lifetime models, such as Weibull or lognormal may be inadequate.

@@

\bibliographystyle{plainnat}
\bibliography{sample}

>>>>

\bigskip
\begin{abstract}
% Consumers have an interest in accurate assessment of product reliability.  However, lifetime data is often sparse and has limited information.  
When conducting lifetime analysis with field data on consumer products, model-based approaches to inference require a model with sufficient flexibility to account for multiple kinds of failure. The causes of these, while not interesting to the consumer per se, can lead to various observed lifetime distributions. Because of this, standard lifetime models, such as Weibull or lognormal may be inadequate. 
Furthermore, when the information carried by lifetime data are limited by sample size, censoring and truncation, estimates can be unstable and suffer from imprecision. These limitations are typical; for example, lifetime data for high-reliability products will naturally tend to be right-censored.

@@

\bibliographystyle{apalike}
\bibliography{sample}
